\documentclass{amsproc}
\usepackage[margin=0.5in]{geometry}
\begin{document}

\section{Statement}
We have $N$ airports with $n_{ij}$ passengers from $i$ to $j$. The
level of infection in the general population is $q \in
(0,1)$. Contrary to the notation used in the main text, we denote
$p_i$ the probability that one infected individual in city $i$ {\it
  will} cause an outbreak. Thus the probability for no outbreak (given
the basal infection incidence $q$) is caused by travel from city $a$
is denoted:
$$
NO(q,a;N) = \prod_{i=1}^{N} (1 - qp_i)^{n_{ai}},
$$

We want to prove that if there is a single $q_0$ that orders the
probabilities $NO(q_0,a;N), NO(q_0,b;N)$ --- then the same order
remains for any other choice of $q \in (0,1)$. Formally, we need to
prove the following implication for all $N \in \mathbb{N}$:

$$
\exists q_0\in (0,1)\ s.t.\ NO(q_0,a;N) \geq NO(q_0,b;N) \Rightarrow \forall q \in (0,1)\ NO(q,a;n) \geq NO(q,b;n).
$$


\section{Proof - Unfortunately this proof is wrong and the statement does not hold}
We continue by induction.

\subsection{Induction Basis}
For the induction basis we want to show that the statement holds for
$N=1$. This amounts to proving the following implication holds:
$$
\exists q_0 \in (0,1)\ s.t.\ (1-q_0p_1)^{n_{a1}} \geq (1-q_0p_1)^{n_{b1}} \Rightarrow  \forall q \in (0,1)\  (1-qp_1)^{n_{a1}} \geq (1-qp_1)^{n_{b1}}.
$$

Taking $\log$ of the LHS, and recalling that $(1-q_0p_1) < 1$, we get
that
\begin{equation*}
n_{a,1} \leq n_{b,1}.
\end{equatlion*}

Consequenctly:

\begin{eqnarray*}
(1-qp_1)^{n_{a,1}} \geq (1-qp_{1})^{n_{b,1}}\ \forall q \in (0,1). 
\end{eqnarray*}
Thus proving the induction basis.


\subsection{Induction Step}
The induction step requires some care. We want to show the following
implication:

\begin{eqnarray*}
  \textbf{If: } &\exists q_0\in (0,1)\ s.t.\ NO(q_0,a;N) \geq NO(q_0,b;N)
  \Rightarrow \forall q\in (0,1)\ NO(q,a;N) \geq NO(q,b;N) \\
  %
  \textbf{Then: } &\exists q_0\in (0,1)\ s.t.\ NO(q_0,a;N+1) \geq
  NO(q_0,b;N+1) \Rightarrow \forall q\in (0,1)\ NO(q,a;N+1) \geq NO(q,b;N+1)
\end{eqnarray*}

Let us assumme \textbf{If}. We need to show the implication in
\textbf{Then} holds. Let $q_0$ such that the left part of
\textbf{Then} holds. Let $q_0 \in (0,1)$ such that $NO(q_0,a;N+1) >
NO(q_0,b;N+1)$. Surely there exists some $i$ for which

\begin{equation*}\label{wlog}
(1-q_0p_i)^{n_{ai}} \geq (1-q_0p_i)^{n_{bi}},
\end{equatlion*}

because otherwise $NO(q_0,a;N+1) < NO(q_0,a;N+1)$. By reshuffling the
indices we can assume without loss of generality, that

\begin{equation*}
(1-q_0p_{N+1})^{n_{a,N+1}} \geq (1-q_0p_{N+1})^{n_{b,N+1}}. 
\end{equatlion*}

Taking $\log$, we get
\begin{equation*}
n_{a,N+1} \leq n_{b,N+1}
\end{equatlion*}

and, consequenctly:
\begin{eqnarray}\label{wlog}
(1-qp_{N+1})^{n_{a,N+1}} \geq (1-qp_{N+1})^{n_{b,N+1}}\ \forall q \in (0,1). 
\end{eqnarray}

Now we are ready to prove the induction step.
\begin{align*}
  \begin{split}
  NO(q,a;N+1) &= \prod_{i=1}^{N+1} (1-qp_i)^{n_{ai}}\\
  %
  &= (1-qp_{N+1})^{n_{a,N+1}} \prod_{i=1}^{N} (1-qp_i)^{n_{ai}}\\
  %
  &\geq (1-qp_{N+1})^{n_{b,N+1}} \prod_{i=1}^{N} (1-qp_i)^{n_{ai}} \text{ (Using \ref{wlog})}\\
  %
  &= (1-qp_{N+1})^{n_{b,N+1}} NO(q,a;N) \text{ (By definition)} \\
  %
  &\geq (1-qp_{N+1})^{n_{b,N+1}} NO(q,b;N) \text{ (Using the LHS of {\bf If})}\\
  %
  &=NO(q,b;N+1) \text{ (By definition)}.
  \end{split}
\end{align*}
This completes the induction step and the proof.
\end{document}
